Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-01-27 paper/main.tex
restructure RSC, LOC, control contrasts

\begin{itemize}
    \item how much details regarding procedure in Sengupta?
    \item ggf. berichten welcher VIS Kontraste jeweils genommen wurde
    \item results allg. kürzen (war nicht ganz einfach)
    \item table of results: how many decimal points?
    \item check if captions of figs and tables now (really) match phrasing
        in intro / method
    \item Simons Kommentare, bei denen ich mitunter anderer Meinung bin

@@

\noindent Discussion
\begin{itemize}
    \item Discussion is restructured
    \item current structure makes a lot things easier/concise/more logical to
        convey, and eventually easier to read and the message to grasp
    \item as Simon stated I would be interesting to discuss differences between
        contrasts (and make wild assumptions) but this will exceed the word
        limit by far
    \item mehr zum Thema VIS? ("best contrast was chosen")
\end{itemize}

@@

\subsubsection{retrosplenial cortex (RSC)}

\todo[inline]{SE: RSC etc: Irgendwie waren die bis zu Diskussion eher ein
afterthought. Daher etwas überraschend, vielleicht in Einleitung und Results
schon mehr bringen; COH: afterthought, for sure; It was highly probable that RSC
would show up but it wasn't aim of the study (had no ROIs for it anyway); imo
this is an issue of ``nice story telling'' vs. HARKing}

% but RSC
Apart from the PPA, we find significantly increased activity in the
retrosplenial cortex (RSC) consistently across contrasts of both stimuli (AD
stimulus: 7 contrasts; AV stimulus: 3 contrasts).
% location functionally defined
The RSC as a scene-selective region is not necessarily spatially congruent with
the anatomically defined retrosplenial cortex [26] (BA 29 and 30)
\citep{epstein2008parahippocampal} but functionally defined as the posterior
medial region that exhibits increased hemodynamic activity to visual scenes and
during mental imagination trough familiar environments [8]
\citep{epstein2008parahippocampal}.
% location
This functionally defined RSC is located in the retrosplenial cortex, and
posterior cingulate region (BA 23 and 31) [51–56], near to the point where the
calcarine sulcus joins the parietal-occipital sulcus
\citep{epstein2008parahippocampal}.

% discussion of what the RSC does
interpretation cf.:
\begin{itemize}
    \item \citep{chrastil2018heterogeneity}
    \item \citep{vann2009what}
    \item \citep{silson2019posterior}
    \item \citep{baldassano2016two}:
    \item RSC appears to be most directly involved in orienting the viewer to
    the structure of the environment (both within and beyond the borders of the
presented image) for the purpose of navigational planning; it encodes both
absolute location and facing direction [Vass and Epstein, 2013; Epstein and
Vass, 2014; Marchette et al., 2014], integrates across views presented in a
panoramic sequence [Park and Chun, 2009], and shows strong familiarity effects
[Epstein et al., 2007a,b].
\end{itemize}

\subsubsection{superior lateral occipital cortex (TOC / OPA?)}

\begin{itemize}
\item Bettencourt (2013). The Role of Transverse Occipital Sulcus in Scene
    Perception
\item Dilks, Kanwisher (2013). The Occipital Place Area Is Causally and
    Selectively Involved in Scene Perception
\item Nasr (2011). Scene-selective cortical regions in human and nonhuman
    primates
\item Dilks (2011). Mirror-image sensitivity and invariance in object \& scene
    processing
\item MacEvoy and Epstein (2007). Position selectivity in scene- and
    object-responsive
\item Grill-Spector (2003). The neural basis of object perception
\item Hasson (2003). Large-scale mirror-symmetry organization
\item Nakamura (2000). Functional delineation of the human occipito-temporal
    areas
\item \citep{baldassano2016two} regarding functional difference pPPA vs. OPA:
    The functional distinction is unclear.
    Previous work has speculated about the purpose of the apparent ventral and
    dorsal ``duplication'' of regions sensitive to large landmarks, proposing
    that it may be related to different output goals (e.g., action planning in
    OPA, object recognition in pPPA)[Konkle and Caramazza, 2013], or to
    different input connections (e.g., lower visual field processing in OPA,
    upper visual field processing in pPPA)[Kravitz et al., 2013; Silson et al.,
    2015].
    OPA and pPPA may also use information from different visual
    eccentricities: OPA processing less peripheral, relatively high-resolution
    environmental features. pPPA processing more peripheral, large-scale
    geometry, and context [Baldassano et al., 2016a]
\end{itemize}

\todo[inline]{in any case: the pattern PPA, RSC, LOC is a usual pattern in the
visual domain; here, it is the usual pattern across across AV and AD contrasts
-> hypothesis for auditory domain? future research and stuff?}

@@

\todo[inline]{imo it should be possible to handle the following two subsections
    in one subsection; à la: GLM + naturalistic stimuli works because
    confounds average (most often) out AND negative control contrasts show
    negative results; except where features of AV + AD were correlated; but
that's actually cool because -> hypothesis}

% ``confounding'' clusters
Despite performing a whole brain analysis, we do not find many [random] clusters
in single contrasts or even systematically across contrasts that hamper the
interpretation of results.\todo{ouff\dots}
% AV: null results regarding attention and eye movements
For example in the AV results, we do not find significant clusters that could be
attributed to cognitive processes like attention or eye movements.\todo{could
already be mentioned in discussion of primary contrasts}

% AD: auditory cortices
Nevertheless, contrasts of the AD stimulus that compare (among others) verbal
hints of the change of a setting (\texttt{se\_new} or \texttt{se\_old}) to all
non-spatial categories (cf. contrasts 2, 3, 6, 7) show significant clusters in
(primary and secondary) auditory cortices.
% averaging vs. nuisance regressors
This suggests that variance correlating with lower level auditory processes was
not averaged out across trials and nuisance regressors did not capture enough
variance.\todo{ouf\dots}
% possible reason
Significant clusters in auditory cortices could be correlating with a possible
change of the soundscape when the narrator of the audio-description (or a cut in
the movie) switches to a another setting.
% concluding statement
Thus, investigators that use model-driven methods to investigate brain functions
using naturalistic stimuli should (extensively) annotate the stimulus material
and test for correlations among variables.

\todo[inline]{concluding statement: essentially "natural stimuli, fuck yeah!;
re-use of existent data; using [and extending] an already existing annotation
for to operationalize a specific perceptual process}

>>>>

\begin{itemize}
    \item how much details regarding procedure in Sengupta?
    \item ggf. berichten welcher VIS Kontraste jeweils genommen wurde
    \item results allg. kürzen (war nicht ganz einfach)
    \item check if captions of figs and tables now (really) match phrasing
        in intro / method
    \item Simons Kommentare, bei denen ich mitunter anderer Meinung bin

@@

\noindent Discussion
\begin{itemize}
    \item Discussion is restructured \& most paragraphs adopted to new structure
    \item as Simon stated I would be interesting to discuss differences between
        contrasts (and make wild assumptions) but this will exceed the word
    limit by far
    \item mehr zum Thema VIS? ("best contrast was chosen")
    \item overall conclusion as a last paragraph or independent section
\end{itemize}

@@

\subsubsection{RSC \& LOC}

\todo[inline]{part regarding RSC \& LOC is now super short; maybe give half a
sentence that this was not focus of the story (but still kinda expected)}

% intro
Apart from the PPA, we find significantly increased activity in the dorsal
precuneus and posterior cingulate region (e.g. retrosplenial cortex; RSC) and
lateral occipital cortex (LOC) across contrasts of both naturalistic stimuli.
% RSC intro
Like the PPA, the RSC (AV stimulus: significant clusters in 3 of 5 contrasts; AD
stimulus: 7 of 8 contrasts) and LOC (AV stimulus: XY of 5 contrasts; AD
stimulus: XY of 8 contrasts) are known to be scene-selective regions (see
\citep{chrastil2018heterogeneity, bettencourt2013role} for reviews).
% conclusion
\todo[inline]{conclusion: what does that say about our results regarding PPA as
a scene-selective region, and audio-visual and auditory naturalistic stimuli in
general?}

\todo[inline]{if we locate a conclusion regarding ``naturalistic stimuli, fuck
yeah'' (+ re-use of existent data) here already, we can add the following part
``not many random clusters'' \& ``control contrasts'' imo elegantly and
shortened here as ``caveats''}

\todo[inline]{``caveats'' = you need extensive annotations and need to know the
    confound structure; but it's the confound structure that leads to the
    hypothesis that changes of the soundscape might also correlate with activity
in the PPA (cf. ``shower thoughts'')}

% some backup text for RSC & LOC
\begin{comment}
% RSC
RSC is located in the retrosplenial cortex, and posterior cingulate region (BA
23 and 31) [51–56], near to the point where the calcarine sulcus joins the
parietal-occipital sulcus \citep{epstein2008parahippocampal}.
%
RSC location functionally defined. In context of scene perception, the RSC is
not necessarily spatially congruent with the anatomically defined retrosplenial
cortex [26] (BA 29 and 30) \citep{epstein2008parahippocampal} but functionally
defined as the posterior medial region that exhibits increased hemodynamic
activity to visual scenes and during mental imagination trough familiar
environments [8] \citep{epstein2008parahippocampal}.

\begin{itemize}
    \item \citep{chrastil2018heterogeneity}
    \item \citep{vann2009what}
    \item \citep{silson2019posterior}
    \item \citep{baldassano2016two}:
    \item RSC appears to be most directly involved in orienting the viewer to
    the structure of the environment (both within and beyond the borders of the
presented image) for the purpose of navigational planning; it encodes both
absolute location and facing direction [Vass and Epstein, 2013; Epstein and
Vass, 2014; Marchette et al., 2014], integrates across views presented in a
panoramic sequence [Park and Chun, 2009], and shows strong familiarity effects
[Epstein et al., 2007a,b].
\end{itemize}

% LOC
\begin{itemize}
\item Bettencourt (2013). The Role of Transverse Occipital Sulcus in Scene
    Perception
\item Dilks, Kanwisher (2013). The Occipital Place Area Is Causally and
    Selectively Involved in Scene Perception
\item Nasr (2011). Scene-selective cortical regions in human and nonhuman
    primates
\item Dilks (2011). Mirror-image sensitivity and invariance in object \& scene
    processing
\item MacEvoy and Epstein (2007). Position selectivity in scene- and
    object-responsive
\item Grill-Spector (2003). The neural basis of object perception
\item Hasson (2003). Large-scale mirror-symmetry organization
\item Nakamura (2000). Functional delineation of the human occipito-temporal
    areas
\item \citep{baldassano2016two} regarding functional difference pPPA vs. OPA:
    The functional distinction is unclear.
    Previous work has speculated about the purpose of the apparent ventral and
    dorsal ``duplication'' of regions sensitive to large landmarks, proposing
    that it may be related to different output goals (e.g., action planning in
    OPA, object recognition in pPPA)[Konkle and Caramazza, 2013], or to
    different input connections (e.g., lower visual field processing in OPA,
    upper visual field processing in pPPA)[Kravitz et al., 2013; Silson et al.,
    2015].
    OPA and pPPA may also use information from different visual
    eccentricities: OPA processing less peripheral, relatively high-resolution
    environmental features. pPPA processing more peripheral, large-scale
    geometry, and context [Baldassano et al., 2016a]
\end{itemize}

\end{comment}

@@

% ``confounding'' clusters
Despite performing a whole brain analysis, we do not find many [random] clusters
in single contrasts or even systematically across contrasts that hamper the
interpretation of results.\todo{ouff\dots}
% AV: null results regarding attention and eye movements
For example in the AV results, we do not find significant clusters that could be
attributed to cognitive processes like attention or eye movements.
% AD: auditory cortices
Nevertheless, contrasts of the AD stimulus that compare (among others) verbal
hints of the change of a setting (\texttt{se\_new} or \texttt{se\_old}) to all
non-spatial categories (cf. contrasts 2, 3, 6, 7) show significant clusters in
(primary and secondary) auditory cortices.
% averaging vs. nuisance regressors
This suggests that variance correlating with lower level auditory processes was
not averaged out across trials and nuisance regressors did not capture enough
variance.\todo{ouf\dots}
% possible reason
Significant clusters in auditory cortices could be correlating with a possible
change of the soundscape when the narrator of the audio-description (or a cut in
the movie) switches to a another setting.
% concluding statement
Thus, investigators that use model-driven methods to investigate brain functions
using naturalistic stimuli should (extensively) annotate the stimulus material
and test for correlations among variables.
